A Formal Model of Checked C

### 2023-01-18 sandp23/evaluation.tex
update.
Adding no-op sandbox experiment

%\input{figures/memoryoverhead}
\Cref{fig:runtimeoverhead} shows the overhead of the partitioned programs.
%It is interesting to see a lot of variance in the runtime overhead.
The runtime overhead is proportional to the execution time 
spent in the sandbox and the number of transitions between~\cregion and the sandbox,
which coincides with the sandbox execution overhead observation in the micro-benchmarks experiments (\Cref{fig:microbenchmarks}).
\Cref{table:conversioneffort} shows the numbers of lines in the sandbox for our partitioned programs.
For~\texttt{ProFTPD}, we used only tainted pointers without code in the sandbox and transitions to/from the sandbox.
Consequently, the overhead is less than 4.2\%.
For~\texttt{UFTPD} and~\texttt{MicroHTTPD}, we sandboxed only request handlers (relatively small)
that parse messages and return the actions that need to be performed.
The server only invokes these handlers on particular requests resulting in less transitions interacting with the sandbox.
As expected, the overhead is also little in these cases.
For~\texttt{TinyBigNum} and~\texttt{Parsons}, the overhead is high because of the relatively large amount of code in sandbox region.
In both applications, we place the frequently used parsing functions in the sandbox 
resulting in a lot of sandbox transitions with most of them in a loop.
The case is slightly different in~\texttt{pnm2png} and~\texttt{png2pnm},
where we made the entire~\code{png} structure tainted, 
which resulted in dynamic checks every time when the~\code{png} struct is accessed.
The result indicates a higher overhead than the non-sandboxing cases and less overhead than the heavy sandboxing cases.
In summary:
\begin{itemize}
  \item Runtime overhead is proportional to the extent of annotated pointers, sandboxed code, and transitions between~\cregion and sandbox.
  \item Using tainted pointers with compiler generated dynamic checks is preferred than placing code in sandbox.
  \item Different C to \systemname conversion methods affect the overhead performance, which is our major future work.
\end{itemize}

>>>>

%\input{figures/memoryoverhead}
\Cref{fig:runtimeoverhead} shows the overhead of the partitioned programs.
%It is interesting to see a lot of variance in the runtime overhead.
The runtime overhead is proportional to the execution time 
spent in the sandbox and the number of transitions between~\cregion and the sandbox,
which coincides with the sandbox execution overhead observation in the micro-benchmarks experiments (\Cref{fig:microbenchmarks}).
\Cref{table:conversioneffort} shows the numbers of lines in the sandbox for our partitioned programs.
For~\texttt{ProFTPD}, we used only tainted pointers without code in the sandbox and transitions to/from the sandbox.
Consequently, the overhead is less than 4.2\%.
For~\texttt{UFTPD} and~\texttt{MicroHTTPD}, we sandboxed only request handlers (relatively small)
that parse messages and return the actions that need to be performed.
The server only invokes these handlers on particular requests resulting in less transitions with the sandbox.
As expected, the overhead is also less in these cases.
For~\texttt{TinyBigNum} and~\texttt{Parsons}, the overhead is high because of the relatively large amount of code in sandbox region.
In both applications, we place the frequently used parsing functions in the sandbox 
resulting in a lot of sandbox transitions with most of them in a loop.
The case is slightly different in~\texttt{pnm2png} and~\texttt{png2pnm},
where we made the entire~\code{png} structure tainted, 
which resulted in dynamic checks every time when the~\code{png} struct is accessed.
In summary, our results indicate that the runtime overhead largely depends on the sandbox.

\noindent\textbf{Overhead of only~\systemname{}.}
To verify the impact of the sandbox on the overall program runtime, we perform a NO-OP sandbox experiment.
Our goal is to measure the runtime overhead introduced ONLY by~\systemname{}.
We perform this experiment by skipping sandboxing.
Specifically, we run the completely annotated program as a regular application without any partitioning.
However, we compile the annotated program with~\systemname compiler, which will add the relevant runtime checks (\sect{subsec:compilerimple}).
We modify the instrumentation on~\code{taint}ed pointers to check for a valid pointer (instead of within sandbox bounds) -- this will add the same amount of checks as in sandboxing case, but the comparison values will be different.

The~\fig{XXX} shows the runtime overhead. The overhead is negligible in all cases.
This shows that~\systemname{} fundamentally has the least overhead.
\aravind{Arun, we should do this experiment. This should be fairly easy.}

%The result indicates a higher overhead than the non-sandboxing cases but much less overhead than the heavy sandboxing cases.
%In summary:
%\begin{itemize}
%  \item Runtime overhead is proportional to the extent of annotated pointers, sandboxed code, and transitions between~\cregion and sandbox.
%  \item Using tainted pointers with compiler generated dynamic checks is preferred than placing code in sandbox.
%  \item Different C to \systemname conversion methods affect the overhead performance, which is our major future work.
%\end{itemize}
